\plaintitle

### 2016-09-12 drafts/labor/cases.tex
renamed files, moved stuff around, adding implications sections

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:Complexity},
  \item \nameref{sec:Slicing}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  \begin{appendices}
% \section{Graveyard}

\endnotetext{
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,
    particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
}
\endnotetext{
\subsection{What forms of work design and worker management are viable?}
\begin{itemize}
  \item researchers have looked at how to increase worker productivity
  (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
  \cite{measuringCrowdsourcingCheng}.
  \item we've also seen people ``embrace error''
  \cite{embracingErrorKrishna}.
  \item still other research has looked into ways to sandbox workers from the context of their work 
  \item but scholarship looking into the design and management of work and workers isn't new;
  lots of research into getting pieceworkers to do work more quickly
  \cite{seymour1954manual}.
  \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
  (echoing similar research on Wikipedia and Mechanical Turk)
  \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
\end{itemize}

@@

    \subsection{The Fallout of Crowd Work}\label{sec:Fallout}
    % If the research exploring and documenting how we can exploit crowd \textit{work} can be described as wide--ranging,
    % the scholarship discussing the ways crowd \textit{workers} have been exploited is more focused;
    \citeauthor{turkopticon} point out the disillusion that companies such as Amazon foster on platforms for work like AMT
    (see also \citeauthor{dynamo}'s work
    continuing in the spirit of this observation to generate collective action to improve worker conditions)
    \cite{turkopticon,dynamo}.
    \citeauthor{uberAlgorithm}
    find similarly that workers on gig work platforms are frustrated by the systems on which they work,
    to say little of the policies which these systems enforce
    \cite{uberAlgorithm}.

@@

    \subsubsection{Low Pay}\label{sec:lowPay}

@@

    \subsubsection{Variable quality work}\label{sec:varQualWork}
    Researchers have struggled with what we might generously call work of ``variable quality''
    along two dimensions.
    The first, to use the characterization of one of these contributions, we can call
    ``understanding malicious behavior''
    \cite{MaliciousCrowdworkersGadiraju}.
    While some work has cast workers as ``malicious'' or at least adversarial parties,
    the evidence thus far suggests that
    workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
    (a topic of discussion to which we'll return later)
    \cite{uberAlgorithm}.
    The second dimension of research in this space generally attempts
    to eke out the highest quality work possible from workers
    given the apparent difficulty in predicting work outcomes
    \cite{embracingErrorKrishna}.

@@

    \subsection{Relationships Between Workers and Managers}\label{sec:relationships}
    Suffice it to say that poor pay and poor work are linked,
    and that we should not be surprised to find this relationship play out online as strongly as it does offline.
    But the poor treatment of workers by managers
    --- both human and algorithmic ---
    do more than affect the economic relationships between workers and employers.
    Here, then, we turn to examine this facet of on--demand work
    and how these dynamics strikingly replicate the relationships
    researchers in labor advocacy encountered in the study of piecework and factory work.

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored,
    but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
    where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant,
    even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.
}
  \theendnotes
  \end{appendices}
  }

>>>>

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:complexity},
  \item \nameref{sec:decomposition}, and
  \item \nameref{sec:relationships}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  }
  % \begin{appendices}
% \section{Graveyard}
\endnotetext{
\section{Cases notes}
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,
    particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
  % }
  % \endnotetext{
  \subsection{What forms of work design and worker management are viable?}
  \begin{itemize}
    \item researchers have looked at how to increase worker productivity
    (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
    \cite{measuringCrowdsourcingCheng}.
    \item we've also seen people ``embrace error''
    \cite{embracingErrorKrishna}.
    \item still other research has looked into ways to sandbox workers from the context of their work 
    \item but scholarship looking into the design and management of work and workers isn't new;
    lots of research into getting pieceworkers to do work more quickly
    \cite{seymour1954manual}.
    \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
    (echoing similar research on Wikipedia and Mechanical Turk)
    \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
  \end{itemize}

@@

    \subsection{The Fallout of Crowd Work}
    % If the research exploring and documenting how we can exploit crowd \textit{work} can be described as wide--ranging,
    % the scholarship discussing the ways crowd \textit{workers} have been exploited is more focused;
    \citeauthor{turkopticon} point out the disillusion that companies such as Amazon foster on platforms for work like AMT
    (see also \citeauthor{dynamo}'s work
    continuing in the spirit of this observation to generate collective action to improve worker conditions)
    \cite{turkopticon,dynamo}.
    \citeauthor{uberAlgorithm}
    find similarly that workers on gig work platforms are frustrated by the systems on which they work,
    to say little of the policies which these systems enforce
    \cite{uberAlgorithm}.

@@

    \subsubsection{Low Pay}

@@

    \subsubsection{Variable quality work}
    Researchers have struggled with what we might generously call work of ``variable quality''
    along two dimensions.
    The first, to use the characterization of one of these contributions, we can call
    ``understanding malicious behavior''
    \cite{MaliciousCrowdworkersGadiraju}.
    While some work has cast workers as ``malicious'' or at least adversarial parties,
    the evidence thus far suggests that
    workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
    (a topic of discussion to which we'll return later)
    \cite{uberAlgorithm}.
    The second dimension of research in this space generally attempts
    to eke out the highest quality work possible from workers
    given the apparent difficulty in predicting work outcomes
    \cite{embracingErrorKrishna}.

@@

    \subsection{Relationships Between Workers and Managers}
    Suffice it to say that poor pay and poor work are linked,
    and that we should not be surprised to find this relationship play out online as strongly as it does offline.
    But the poor treatment of workers by managers
    --- both human and algorithmic ---
    do more than affect the economic relationships between workers and employers.
    Here, then, we turn to examine this facet of on--demand work
    and how these dynamics strikingly replicate the relationships
    researchers in labor advocacy encountered in the study of piecework and factory work.

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored,
    but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
    where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant,
    even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.
  }
  % \theendnotes
  % \end{appendices}

### 2016-09-12 drafts/labor/complexity.tex
renamed files, moved stuff around, adding implications sections

\subsubsection[finding crowdwork's limits]{Achieving greater complexity
\joke{ --- or ``making crowd--work \textit{yuge}''}
}\label{sec:Complexity}
% crowd weaver, aditya's book

@@

  \clearpage
  \nobalance{}
  \begin{appendices}
  \section{Paragraph graveyard}
    \topic{\joke{great} topic sentence here.}
    \citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
    exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
    While some of this work doesn't strictly fall under ``crowdsourcing'',
    the [scientific] management of the self as a worker
    (of sorts)
    will prove relevant as we trace the literature surrounding piecework.

@@

  \citeauthor{10.2307/23702539} also argues that
  a significant obstacle to the introduction of piecework in railroad shops was
  the resistance of workers
  (the other being the resistance of management (for different and varying reasons)).
  In the cases of online platforms like AMT and digitally mediated platforms like Uber,
  where in both cases workers rarely
  if ever
  interact face--to--face and
  opportunities for coordination and collective action are severely limited,
  we should expect to see
  the challenges stymieing collective action
  that we see in \citeauthor{dynamo} and elsewhere
  \cite{10.2307/23702539,dynamo}.
  \end{appendices}

}

>>>>

\subsubsection[finding crowdwork's limits]{Achieving greater complexity}\label{sec:complexity}
\ali{maybe a subssubsubsusbsubsection on the result/implication?
more people can make crowd tasks, but the algiorithmic manag}

@@

  \clearpage
  \nobalance{}
  }
  \endnotetext{
  \section{Complexity notes}
    \topic{\joke{great} topic sentence here.}
    \citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
    exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
    While some of this work doesn't strictly fall under ``crowdsourcing'',
    the [scientific] management of the self as a worker
    (of sorts)
    will prove relevant as we trace the literature surrounding piecework.

@@

  \citeauthor{10.2307/23702539} also argues that
  a significant obstacle to the introduction of piecework in railroad shops was
  the resistance of workers
  (the other being the resistance of management (for different and varying reasons)).
  In the cases of online platforms like AMT and digitally mediated platforms like Uber,
  where in both cases workers rarely
  if ever
  interact face--to--face and
  opportunities for coordination and collective action are severely limited,
  we should expect to see
  the challenges stymieing collective action
  that we see in \citeauthor{dynamo} and elsewhere
  \cite{10.2307/23702539,dynamo}.
}

### 2016-09-12 drafts/labor/decomposition.tex
renamed files, moved stuff around, adding implications sections

\subsubsection[slicing work into smaller parts]{Slicing work smaller
\joke{ --- or ``putting the {\tiny `micro'} in microwork''}
}\label{sec:Slicing}

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography

  \clearpage
  \nobalance{}
  \begin{appendices}
    \section{Paragraph graveyard}
    The finding here is that
    crowdwork can be more carefully micro--managed than piecework could be,
    and that this is a double--edged sword:
    we can effectively give feedback to workers on everything they do,
    but this is emboldening us to try to
    over--manage workers just as piecework tried to do.

@@

  \end{appendices}
}

>>>>

\subsubsection[the decomposition of work]{The Decomposition of Work}\label{sec:decomposition}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography

  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Slicing notes}
    The finding here is that
    crowdwork can be more carefully micro--managed than piecework could be,
    and that this is a double--edged sword:
    we can effectively give feedback to workers on everything they do,
    but this is emboldening us to try to
    over--manage workers just as piecework tried to do.

@@

  }

### 2016-09-12 drafts/labor/relationships.tex
renamed files, moved stuff around, adding implications sections

\subsubsection[worker volatility]{Volatile quality and availability? How much can you deal with?}
\label{sec:flexibility}

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  % \nobalance{}

  \begin{appendices}
  A number of researchers have identified
  worker attrition,
  variability of worker performance,
  and uncertainty about good versus bad--faith actors as open questions of crowdwork
  \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
  \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
  \& workers who are merely responding in kind to bad requesters
  --- and the broader questions surrounding
  the roles that requesters as well as workers should play ---
  but let it suffice to say that
  requesters have been trying to understand and manage what appears to them as inconsistent work.
  Their ways of responding to that variance in work quality has largely involved
  making the work more flexible and resilient to work
  (although some work has gone into investigating the causes, rather than treating the symptoms)}

@@

  In the field of piecework,
  the research covering this topic has both explored
  a breadth of tasks that might be rendered doable by piecemeal workers
  \textit{as well as} longitudinally documented the success of these approaches.
  Here, we

\end{appendices}
}

\end{document}

>>>>

\subsubsection[the relationships of workers]{???}
\label{sec:relationships}

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Flexibility notes}
    A number of researchers have identified
    worker attrition,
    variability of worker performance,
    and uncertainty about good versus bad--faith actors as open questions of crowdwork
    \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
    \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
    \& workers who are merely responding in kind to bad requesters
    --- and the broader questions surrounding
    the roles that requesters as well as workers should play ---
    but let it suffice to say that
    requesters have been trying to understand and manage what appears to them as inconsistent work.
    Their ways of responding to that variance in work quality has largely involved
    making the work more flexible and resilient to work
    (although some work has gone into investigating the causes, rather than treating the symptoms)}

@@

    In the field of piecework,
    the research covering this topic has both explored
    a breadth of tasks that might be rendered doable by piecemeal workers
    \textit{as well as} longitudinally documented the success of these approaches.
    Here, we \ali{\dots?}
}
\theendnotes
\end{document}

### 2016-09-12 drafts/labor/trackingWork.tex
slicing and flexibility spin-off
complexity and some slicing stuff
more changes
renamed files, moved stuff around, adding implications sections

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences to make it easier to skim/diagnose logical issues
\newcommand{\joke}[1]{{\color{JokeGreen}#1}} % if you're in a subfile, make the joke JokeGreen colored so people know I'm being funny!
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\maketitle
\begin{abstract}
  With growing attention toward on--demand labor
  --- ranging from the ``sharing economy'' to information work ---
  scholars have made connections to various frameworks 
  and mechanisms such as worker advocacy, empowerment, and Taylorism,
  to make sense of our observations of
  on--demand work and the workers that power this movement.
  We argue that the literature surrounding ``piecework''
  informs and even predicts both the contributions
  that have been made toward the development of on--demand labor and crowd work
  as well as the fallout among workers and researchers
  with regard to the disillusionment and alienation of work.

  After evaluating this framing
  through a series of case studies,
  we look to the future
  to identify worthwhile questions and
  points of inquiry, such as the movement toward factories,
  that researchers in social computing should consider
  as we attempt to anticipate and perhaps shape the future of work.
\end{abstract}

@@

\keywords{\plainkeywords}
\subfile{introduction.tex}
\subfile{cases.tex}

\section{The Bleak Future of Crowd Work}
We've traced a path from piecework itself through
the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
in tracing this process, we touched on the relationships between decomposition,
work \& worker abstraction,
flexibility, and followed through both the general fallout of crowd work in the research community
as well as the fallout between workers and the managers and other external parties
--- including researchers.

@@

\section{Conclusion}
\citeauthor{crowdworkFuture} discussed many of the challenges and problems in crowd work in \citeyear{crowdworkFuture},
but didn't necessarily situate the notion of crowd work in a broader context.
This paper attempts to fill that gap, and in doing so hopes
to give the research community theoretical grounding to work with and within on--demand labor more successfully.
But more than that, we hope to have addressed important questions to inform how we actually might make crowd work
a career in which we want our children to work.

>>>>

\usepackage{zref-xr}
\usepackage{zref-xr}
\zxrsetup{%
  tozreflabel=false, % not needed, since `zref` is not used otherwise
  toltxlabel=true, % classical LaTeX labels that can be referenced with \ref, \pageref
}
\zexternaldocument{cases.tex}% star form: only LaTeX labels are imported

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{Piecework's perspective.}
\newcommand{\crowdworkpers}{Crowdwork's perspective.}
\newcommand{\whatchanged}{What's changed.}
\newcommand{\implication}{Implications for crowdwork.}

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences to make it easier to skim/diagnose logical issues
\newcommand{\joke}[1]{{\color{JokeGreen}#1}} % if you're in a subfile, make the joke JokeGreen colored so people know I'm being funny!
\onlyinsubfile{
  \hypersetup{
    citecolor  = blue,
    linkcolor  = blue,
  }
}

\renewcommand{\footnotesize}{\normalsize} % i don't need small text! (no but really remove this before submitting)
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\maketitle

% Abstract time
\subfile{abstract.tex}

@@

\keywords{\plainkeywords}
\subfile{introduction.tex}
\subfile{piecework_lit.tex}
\subfile{cases.tex}

\clearpage
\nobalance{}
\endnotetext{
  \section{The Bleak Future of Crowd Work}
  We've traced a path from piecework itself through
  the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
  in tracing this process, we touched on the relationships between decomposition,
  work \& worker abstraction,
  flexibility, and followed through both the general fallout of crowd work in the research community
  as well as the fallout between workers and the managers and other external parties
  --- including researchers.

@@

  \section{Conclusion}
  \citeauthor{crowdworkFuture} discussed many of the challenges and problems in crowd work in \citeyear{crowdworkFuture},
  but didn't necessarily situate the notion of crowd work in a broader context.
  This paper attempts to fill that gap, and in doing so hopes
  to give the research community theoretical grounding to work with and within on--demand labor more successfully.
  But more than that, we hope to have addressed important questions to inform how we actually might make crowd work
  a career in which we want our children to work.
}
\theendnotes
